Rotations and Insecticide Resistance initial plots

### 2017-11-21 inst/documents/rotations_notes.Rmd
commenting out add_gens_under50 calc because of NSE error

@@

>>>>

ARG! got migration seeming like it's working

BUT now have come across non-standard-evaluation error in run_rot()

Draft that is sposed to help explain :
http://rpubs.com/lionel-/programming-draft
and posts in here :
https://community.rstudio.com/t/should-tidyeval-be-abandoned/2238/37

I could remove the generations under 50 bit for now to try to get run_rot() working again.

removed add_gens_under50 and now run_rot() does run.

@@

# programing with dplyr
http://dplyr.tidyverse.org/articles/programming.html
